Transform and Tell:\\The News Image Caption Writer That Remembers Rare Names

### 2019-11-13 paper/section_3_model.tex
Add new shortcut commands

For the image, we feed it through a pretrained ResNet-152 model
\cite{He2016ResNet} and use the output of the final block, just before the
pooling layer, as the image embedding $\bx_I \in \mathbb{R}^{2048 \times 49}$.
The embedding forms a 7 by 7 block, allowing the transformer to attend to 49
different patches in the image.

@@

For the article, we use RoBERTa \cite{Liu2019RoBERTaAR} to encode the text.
RoBERTa is a language representation model that provides pretrained contextual
embeddings for text. It consists of 24 layers of bidirectional transformer
blocks. It is a more carefully trained BERT \cite{Devlin2019BERT} model.

Unlike GloVe \cite{Pennington2014Glove} and word2vec
\cite{Mikolov2013DistributedRO} embeddings, where each word has exactly one
representation, the bidirectionality and the attention mechanism in the
transformer allow a word to have different vector representations depending on
the surrounding context.

@@

Given an input of length $S$, the pretrained RoBERTa encoder will return 25
sequences of embeddings, $\bg_i \in \mathbb{R}^{2048 \times S}$ for $i \in
\{0,1, 2,...,24\}$. This includes the initial uncontextualized embeddings and
the output of each of the 24 layers. Inspired by Tenney \etal
\cite{Tenney2019BertRT}, who showed that different layers in BERT represent
different steps in the traditional NLP pipeline, we take a weighted sum
across all layers to obtain the article embedding:
\begin{IEEEeqnarray*}{lCl}
   \bx_T &=& \sum_{i=0}^{24} \alpha_i \bg_i
\end{IEEEeqnarray*}
where $\bx_T \in \mathbb{R}^{1024 \times S}$ is the article embedding
and $\alpha_i$ are learnable weights.

@@

@@

To embed the faces, we first use MTCNN \cite{Zhang2016JointFD} to detect the
face bounding boxes. We then select the top $M$ faces and feed them through a
FaceNet model \cite{Schroff2015FaceNetAU}, pretrained on the VGGFace2 dataset
\cite{Cao2017VGGFace2AD}, to obtain a face embedding $\bx_F \in
\mathbb{R}^{512 \times M}$ where $M$ is the number of faces.

@@

>>>>

For the image, we feed it through a pretrained ResNet-152 model
\cite{He2016ResNet} and use the output of the final block, just before the
pooling layer, as the image embedding $\bX_I \in \mathbb{R}^{2048 \times 49}$.
The embedding forms a 7 by 7 block, allowing the transformer to attend to 49
different patches in the image.

@@

For the article, we use RoBERTa \cite{Liu2019RoBERTaAR} to encode the text.
RoBERTa, a more carefully trained BERT \cite{Devlin2019BERT}, is a language
representation model that provides pretrained contextual embeddings for text.
Unlike GloVe \cite{Pennington2014Glove} and word2vec
\cite{Mikolov2013DistributedRO} embeddings, where each word has exactly one
representation, the bidirectionality and the attention mechanism in the
transformer allow a word to have different vector representations depending on
the surrounding context.

@@

@@

The RoBERTa encoder provides gives us the article embedding $\bX_T \in
\mathbb{R}^{1024 \times S}$ where $S$ is the number of tokens.

@@

To embed the faces, we first use MTCNN \cite{Zhang2016JointFD} to detect the
face bounding boxes. We then select the top $M$ faces and feed them through a
FaceNet model \cite{Schroff2015FaceNetAU}, pretrained on the VGGFace2 dataset
\cite{Cao2017VGGFace2AD}, to obtain a face embedding $\bX_F \in
\mathbb{R}^{512 \times M}$ where $M$ is the number of faces.

@@

\subsubsection{Mixing RoBERTa layers}
RoBERTa consists of 24 layers of bidirectional transformer blocks. Given an
input of length $S$, the pretrained RoBERTa encoder will return 25 sequences of
embeddings, $\bG_i \in \mathbb{R}^{2048 \times S}$ for $i \in \{0,1,
2,...,24\}$. This includes the initial uncontextualized embeddings and the
output of each of the 24 layers. Inspired by Tenney \etal
\cite{Tenney2019BertRT}, who showed that different layers in BERT represent
different steps in the traditional NLP pipeline, we take a weighted sum across
all layers to obtain the article embedding:
\begin{IEEEeqnarray*}{lCl}
   \bX_T &=& \sum_{i=0}^{24} \alpha_i \bG_i
\end{IEEEeqnarray*}
where $\bx_T \in \mathbb{R}^{1024 \times S}$ is the article embedding
and $\alpha_i$ are learnable weights.
